An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-06-30 poly-embed-journal/jmlr_cover_letter/jmlr_coverletter.tex
cover

\begin{document}
\hfill{\today}

Journal of Machine Learning Research

@@

We are writing to submit our manuscript ``An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates'' to the \emph{Journal of Machine Learning Research}.

@@

Our manuscript extends the conference publication \emph{An Embedding Framework for Consistent Polyhedral Surrogates} (NeurIPS 2019) and incorporates roughly half the results from \emph{Surrogate Regret Bounds for Polyhedral Losses} (NeurIPS 2021).
We have substantially rewritten and reorganized these papers, as well as adding entirely new results (\S 6, \S 7, \S E).
For example, \S 6 shows the equivalence of several natural notions of non-redundancy, and \S 7 uses our framework to show that indirect elicitation is equivalent to consistency for polyhedral surrogates.

@@

Reviewers:
\begin{itemize}
    \item Bob Williamson, University of T\"ubingen (\url{bob.williamson@uni-tuebingen.de})
    \item Shivani Agarwal, University of Pennsylviania (\url{ashivani@seas.upenn.edu})
    \item Alex Nowak-Vila, Owkin (\url{alex.nowak-vila@inria.fr})
    \item First Lastname, Institution (first.lastname@institution.edu)
    \item First Lastname, Institution (first.lastname@institution.edu)
\end{itemize}

@@

As the corresponding author, I confirm that none of the co-authors listed below have a conflict of interest with the action editors and referees suggested above. Further, I confirm that all co-authors below consent to my submission of this manuscript to the \emph{Journal of Machine Learning Research}.

@@

Jessie Finocchiaro (University of Colorado Boulder)\\
Rafael Frongillo (University of Colorado Boulder)\\
Bo Waggoner (University of Colorado Boulder)

>>>>

\begin{document}
Journal of Machine Learning Research \hfill \today

@@

We are writing to submit our manuscript ``An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates'' to the \emph{Journal of Machine Learning Research (JMLR)}.

@@

Our manuscript extends the conference publication \emph{An Embedding Framework for Consistent Polyhedral Surrogates} (NeurIPS 2019) and incorporates roughly half the results from \emph{Surrogate Regret Bounds for Polyhedral Losses} (NeurIPS 2021).
We have substantially rewritten and reorganized these papers, streamlined the presentation, adjusted the core definitions slightly to make the results more intuitive and elegant, etc., all with the goal of laying out the definitive version of the embedding framework.
We also added entirely new examples and results (\S 5, \S 6, \S 7, \S E).
For example, \S 6 shows the equivalence of several natural notions of non-redundancy, and \S 7 uses our framework to show that indirect elicitation is equivalent to consistency for polyhedral surrogates.

@@

Reviewers:
\begin{itemize}
    \item Bob Williamson, University of T\"ubingen (\url{bob.williamson@uni-tuebingen.de}
    \item Shivani Agarwal, University of Pennsylviania (\url{ashivani@seas.upenn.edu})
    \item Alex Nowak-Vila, Owkin (\url{alex.nowak-vila@inria.fr})
    \item Clayton Scott
    \item Harish Ramaswamy
      % \item Pranjal Ashwathi (see recently published ICML paper) <-- could be great, but I'd have to look into their work more; seemed more on the PAC learning side at first glance, but lots of "consistency" and "surrogates" so maybe a good fit
      % These are either too much of a stretch or too junior I think -- journal reviewers are usually more senior, though students definitely do it now and then
    % \item Yutong Wang
    % \item Han Bao, University of Tokyo / RIKEN AIP (first.lastname@institution.edu)
    % \item Authors of this paper: \url{https://arxiv.org/pdf/2202.02193.pdf} -- bit of a stretch
    % \item Satyen Kale
\end{itemize}

@@

We confirm that none of the co-authors listed below have a conflict of interest with the action editors and referees suggested above.
(Bob Williamson was a member of the first author's dissertation committee but we did not consider that a conflict.)
All co-authors consent to this submission to JMLR.

@@

Jessie Finocchiaro (University of Colorado Boulder), corresponding author\\
Rafael Frongillo (University of Colorado Boulder)\\
Bo Waggoner (University of Colorado Boulder)
